Developing ShinyMICE

### 2019-12-16 Presentation/Presentation.Rmd
update presentation after mice meeting

## Algorithmic convergence
<br><br>

<center>
<img src="figures/traceplot.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Mock code
```{r eval=FALSE}
simulation <- function() {
  mvtnorm(X,Z1,Z2) %>% 
  mutate(Y~X+Z1+Z2) %>% 
  for (max_iterations in 1:100) {
    ampute() %>% 
    impute() %T% 
    convergence_diagnostics %>% 
    lm(Y~X+Z1+Z2) %>% 
    pool %>% 
    simulation_diagnostics %>% 
    c(., convergence_diagnostics)
  }
}

@@

## Results

<center>
<img src="figures/results.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results | simulation diagnostics versus convergence diagnostics

```{r echo=FALSE}
dat %>% select("It.", "bias", "CIW", "cov", "R_mean_X", "AC_mean_X") %>% round(3) %>% datatable(options = list(pageLength = 5), rownames = FALSE)
```

>>>>

## Algorithmic convergence
<center>
<img src="figures/non-conv.png" alt="HTML5 Icon" width = 77%>
<br>

@@

## Mock code | 
Steps in the simulation study
```{r eval=FALSE}
simulation <- function() {
  mvtnorm(X,Z1,Z2) %>% 
  mutate(Y~X+Z1+Z2) %>% 
  for (max_iterations in 1:100) {
    ampute() %>% 
    impute() %T% 
    convergence_diagnostics %>% 
    lm(Y~X+Z1+Z2) %>% 
    pool %>% 
    simulation_diagnostics %>% 
    c(., convergence_diagnostics)
  }
}

@@

## Simulation diagnostics
<center>
<img src="figures/results_sim.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Convergence diagnostics
<center>
<img src="figures/results_conv.png" alt="HTML5 Icon" width = 100%>
<br>

## Results 
<center>
<img src="figures/results_sim_conv.png" alt="HTML5 Icon" width = 100%>
<br>

## Results | Simulation diagnostics versus convergence diagnostics
```{r echo=FALSE}
dat %>% select("It.", "bias", "CIW", "cov", "R_mean_X", "AC_mean_X") %>% round(3) %>% datatable(options = list(pageLength = 5), rownames = FALSE)
```
